You have more money in your wallet. This does not mean you will spend extra on food

### 2024-04-16 paper/paper.qmd
updated the data_simulate file

In @sec-data, we discuss the data we used for this project, including information of the software and packages used. This is followed any a explanation of the models that we used, which can be found in @sec-model. In @sec-res, we present the results of the models and @sec-dis, we interpret these results, and consider how savings, consumer preference and elasticies play into this discussion on food expenditure and income. We finish the project with weaknesses and potential areas of improvement in the future.

@@

@tbl-3 has discovered that for every billion-dollar rise in disposable income, the average expenditure on food increases by an amount ranging from 20 million USD to 70 million USD. This validates our hypothesis, suggesting a direct correlation between income and food consumption. According to the models, this translates to an economic significance of $70,000,000/$1,000,000,000, equivalent to a 7% increase. In the following section, we talk about the reasons behind relatively low economic significance, exploring the impact of savings, consumer behavior and elastiticies, followed by potential weaknesses in our paper.

@@

The income and price elasticities of food are crucial factors in understanding why there's not much change in food spending despite changes in income. Income elasticity measures how much food demand shifts when income changes, while price elasticity assesses the impact of price changes on food demand.

@@

In essence, these findings show that there's only a modest increase in food demand as income rises and a moderate decrease as food prices go up. Consequently, changes in income don't lead to significant shifts in food demand.

@@

This distortion poses challenges for accurately estimating our target variable or estimand. Unforeseen economic fluctuations during the pandemic may skew the true relationship we seek to understand, reducing the model's external validity. The unique nature of the pandemic's shocks further limits the model's generalizability, especially considering variations in social benefit policies and lockdown measures among different countries. Consequently, applying our model to another country within the same timeframe may yield unreliable results due to differing policy responses to COVID-19.

In future iterations, a narrower timeframe excluding such large-scale global shocks would be prudent. This approach aims to enhance the model's external validity and clarify the estimand we are pursuing.

>>>>

@@

@tbl-3 has discovered that for every billion-dollar rise in disposable income, the average expenditure on food increases by an amount ranging from 20 million USD to 70 million USD. This validates our hypothesis, suggesting a direct correlation between income and food consumption. According to the models, this translates to an economic significance of $20,000,000/$1,000,000,000, equivalent to a 2% increase. In the following section, we talk about the reasons behind relatively low economic significance, exploring the impact of savings, consumer behavior and elastiticies, followed by potential weaknesses in our paper.

@@

The income and price elasticities of food are crucial factors in understanding why there is not much change in food spending despite changes in income. Income elasticity measures how much food demand shifts when income changes, while price elasticity assesses the impact of price changes on food demand.

@@

In essence, these findings show that there's only a modest increase in food demand as income rises and a moderate decrease as food prices go up. This suggests changes in income do nott lead to significant shifts in food demand.

@@

This distortion poses challenges for accurately estimating our target variable or estimand. Unforeseen economic fluctuations during the pandemic may skew the true relationship we seek to understand, reducing the model's external validity. The unique nature of the pandemic's shocks further limits the model's generalizability, especially considering variations in social benefit policies and lockdown measures among different countries. Consequently, applying our model to another country within the same time frame may yield unreliable results due to differing policy responses to COVID-19.

In future iterations, a narrower time frame excluding such large-scale global shocks would be prudent. This approach aims to enhance the model's external validity and clarify the estimand we are pursuing.
